# Introduction {#intro}

This is my first bookdown, ... and a sandbox to test its features. I started from [here](http://seankross.com/2016/11/17/How-to-Start-a-Bookdown-Book.html).

You can reference chapters using \@ref(intro). Figures and tables are in their own environments:

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

In the [example minimum repo](https://github.com/rstudio/bookdown-demo) there is an example of deployment using Travis-CI.

If some computation is time consuming, we could consider to cache it:

```{r important-computing, cache=TRUE}
# A verrry long computation!
1 + 1
```

To number equations and allow to refer to them, use an `equation` environment and label them with the syntax `(\#eq:label)`:

\begin{equation} 
  f\left(k\right) = \binom{n}{k} p^k\left(1-p\right)^{n-k}
  (\#eq:binom)
\end{equation} 

... and here, I refer to eq. \@ref(eq:binom). In the vase equations are not labelled, use the `equation*` environment instead.

To makes parts in the book, use `# (PART) Part I {-}` just before the first title of that part. Also, you can use `# 5APPENDIX) Appendix {-}` just before appendices titles.

Text reference is especially useful for long captions, or captions with special formattings.

(ref:foo) This is my caption with **formatting**...

```{r foo, fig.cap='(ref:foo)'}
plot(cars)  # a scatterplot
```

**TODO:** browse the bookdown book from 2.4 Figures on....

